% !TEX root = SystemTemplate.tex
\section{Mechanical Log}


\subsection{UAV}
\begin{description}

\item SPRINT 1

\item [9/14/15]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}

\item [9/21/15]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}

\item [9/28/15]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}

\item SPRINT 2

\item [10/12/15]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}

\item [10/19/15]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}

\item [10/26/15]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}

\item SPRINT 3

\item [11/9/15]  Received the Turnigy Talon Hexcopter and got the frame put together. \hfill{Dylan Geyer}

\item [11/11/15] Attached the 6 DC Motors and Electronic speed controllers to each arm of the frame. Noted that there may not be enough room on the base plate of the hexcopter to mount two GPS modules a flight controller and an ODroid. Possible looking at 3D Printing a larger center plate to attach all of the arms to. I burned my fingers a lot trying to solder the ESC's to the motors.

\item [11/16/15]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}

\item [11/23/15]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}

\item SPRINT 3.5

\item [12/21/15]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}

\item [12/28/15]  New base plates for craft was printed and assembled. There is now plenty of room for GPS stands, Flight Controller, and ODroid. Printed base plates are temporary until carbon plates can be made.  

\item [1/4/16]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}

\item SPRINT 4

\item [1/18/16]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}

\item [1/25/16]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}

\item [2/1/16]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}

\item SPRINT 5

\item [2/15/16]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}

\item [2/22/16]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}

\item [2/29/16]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}

\item SPRINT 6

\item [3/21/16]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}

\item [3/28/16]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}

\item [4/4/16]  Ran modified filter on data sets 1 - 6.  Results were ... \hfill{First Last}
\end{description}