 \documentclass[11pt]{beamer}
\usetheme{Warsaw}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}
%\usepackage[latin1]{inputenc}

\author{Team Expeditus}
\title{UAV Autonomous Landing}
%\setbeamercovered{transparent} 
%\setbeamertemplate{navigation symbols}{} 
%\logo{} 
\institute{SDSMT MCS} 
%\date{} 
%\subject{} 
\begin{document}

\begin{frame}
\titlepage
\end{frame}

%\begin{frame}
%\tableofcontents	
%\end{frame}

\begin{frame}{Introduction}
\textbf{UAV Autonomous Landing Project}\\
\vspace{12mm}
\textbf{Team Expeditus}\\
Jonathan Dixon, Dylan Geyer, Christopher Smith, Steven Huerta\\ 
\vspace{6mm}
\textbf{Sponsor}\\
Dr. Larry Pyeatt\\
\end{frame}

\begin{frame}{Project Overview}
\textbf{Goal}\\
\begin{itemize}
\item receive a set of waypoints
\item autonomously take-off
\item navigate through waypoints
\item return to launch pad
\item land on the pad with the correct orientation
\end{itemize}
\vspace{6mm}
\textbf{Limitations}\\
\begin{itemize}
\item landing platform is a fixed position
\item landing platform is a stable, horizontal surface
\item environment is ideal(no wind, gps available, no obstacles)
\end{itemize}
\end{frame}


\begin{frame}{User Stories}

\begin{itemize}
\item \textbf{User 1(U-1):}\\ As a user, I want to communicate the waypoints to the UAV.
\item \textbf{Owner 1(O-1):}\\ As an owner, I want the UAV to autonomously take-off from the landing pad.
\item \textbf{Owner 2(O-2):}\\ As an owner, I want the UAV to autonomously navigate through a set of waypoints.
\item \textbf{Owner 3(O-3):}\\ As an owner, I want the UAV to autonomously return to the location of the landing pad.
\item \textbf{Owner 4(O-4):}\\ As an owner, I want the UAV to autonomously land on the landing pad without damaging the craft.
\item \textbf{Owner 5(O-5):}\\ As an owner, I want the UAV to autonomously land on the landing pad with the correct orientation.
\item \textbf{Common:}\\ Tasks relating to more than one user story(i.e. resolving dependencies).
\end{itemize}

\end{frame}

\begin{frame}{U-1}
\textbf{As a user, I want to communicate the waypoints to the UAV.}
\begin{tabular}{| p{1cm} | lp{2cm} | cp{2cm} | cp{1cm} |}\hline
Task No. & Task & Date Completed & Sprint\\\hline
1 & Review previous method/interface for communicating coordinates to UAV. & 10/05/15 & 1 \\\hline
2 & Review code that communicates with quadrotor & 10/16/15 & 2 \\\hline
3 & Review code that allows a user to input waypoints & 10/16/15 & 2\\\hline

\end{tabular}
\end{frame}


\begin{frame}{O-1}
\textbf{As a user, I want to communicate the waypoints to the UAV.}
\begin{tabular}{| p{1cm} | lp{2cm} | cp{2cm} | cp{1cm} |}\hline
Task No. & Task & Date Completed & Sprint\\\hline
1 & Review previous method/interface for communicating coordinates to UAV. & 10/05/15 & 1 \\\hline
2 & Review code that communicates with quadrotor & 10/16/15 & 2 \\\hline
3 & Review code that allows a user to input waypoints & 10/16/15 & 2\\\hline

\end{tabular}
\end{frame}


\begin{frame}{O-2}
\textbf{As a user, I want to communicate the waypoints to the UAV.}
\begin{tabular}{| p{1cm} | lp{2cm} | cp{2cm} | cp{1cm} |}\hline
Task No. & Task & Date Completed & Sprint\\\hline
1 & Review previous method/interface for communicating coordinates to UAV. & 10/05/15 & 1 \\\hline
2 & Review code that communicates with quadrotor & 10/16/15 & 2 \\\hline
3 & Review code that allows a user to input waypoints & 10/16/15 & 2\\\hline

\end{tabular}
\end{frame}


\begin{frame}{O-3}
\textbf{As a user, I want to communicate the waypoints to the UAV.}
\begin{tabular}{| p{1cm} | lp{2cm} | cp{2cm} | cp{1cm} |}\hline
Task No. & Task & Date Completed & Sprint\\\hline
1 & Review previous method/interface for communicating coordinates to UAV. & 10/05/15 & 1 \\\hline
2 & Review code that communicates with quadrotor & 10/16/15 & 2 \\\hline
3 & Review code that allows a user to input waypoints & 10/16/15 & 2\\\hline

\end{tabular}
\end{frame}


\begin{frame}{O-4}
\textbf{As a user, I want to communicate the waypoints to the UAV.}
\begin{tabular}{| p{1cm} | lp{2cm} | cp{2cm} | cp{1cm} |}\hline
Task No. & Task & Date Completed & Sprint\\\hline
1 & Review previous method/interface for communicating coordinates to UAV. & 10/05/15 & 1 \\\hline
2 & Review code that communicates with quadrotor & 10/16/15 & 2 \\\hline
3 & Review code that allows a user to input waypoints & 10/16/15 & 2\\\hline

\end{tabular}
\end{frame}


\begin{frame}{O-5}
\textbf{As a user, I want to communicate the waypoints to the UAV.}
\begin{tabular}{| p{1cm} | lp{2cm} | cp{2cm} | cp{1cm} |}\hline
Task No. & Task & Date Completed & Sprint\\\hline
1 & Review previous method/interface for communicating coordinates to UAV. & 10/05/15 & 1 \\\hline
2 & Review code that communicates with quadrotor & 10/16/15 & 2 \\\hline
3 & Review code that allows a user to input waypoints & 10/16/15 & 2\\\hline

\end{tabular}
\end{frame}


\begin{frame}{C}
\textbf{As a user, I want to communicate the waypoints to the UAV.}
\begin{tabular}{| p{1cm} | lp{2cm} | cp{2cm} | cp{1cm} |}\hline
Task No. & Task & Date Completed & Sprint\\\hline
1 & Review previous method/interface for communicating coordinates to UAV. & 10/05/15 & 1 \\\hline
2 & Review code that communicates with quadrotor & 10/16/15 & 2 \\\hline
3 & Review code that allows a user to input waypoints & 10/16/15 & 2\\\hline

\end{tabular}
\end{frame}


\begin{frame}{Hardware Requirements}
\begin{itemize}
\item ODroid XU4
\item Pixhawk Flight Controller
\item GPS peripheral
\item Camera
\item Battery
\item UAV(Frame, Motors, ESCs, Power Distribution Board)
\end{itemize}

\end{frame}

\begin{frame}{Software Requirements}
\begin{itemize}
\item Mavlink
\item OpenCV
\item Robot Operating System(ROS) Indigo/Jade Distro
\item Ubuntu 14.04
\end{itemize}

\end{frame}


\begin{frame}{Sprint 1}
	\large{\textbf{Sprint 1 - Successes}}
\begin{itemize}
	\item Revised project scope
	\item Product Backlog - User Stories
	\item Setup Development Environment
	\item Review previous years hardware and software
\end{itemize}

	\large{\textbf{Sprint 1 - Setbacks}}
	\begin{itemize}
		\item Previous years UAV unusable
		\item Previous years flight code unusable
	\end{itemize}
\end{frame}


\begin{frame}{Sprint 2}
	\large{\textbf{Sprint 2 - Successes}}
	\begin{itemize}
		\item Visual Homography Code repurposed
		\item Created simulation environment
		\item Ordered parts for new Hex-copter
	\end{itemize}
	\large{\textbf{Sprint 2 - Setbacks}}
	\begin{itemize}
		\item Simulation only supports manual control
	\end{itemize}
\end{frame}


\begin{frame}{Sprint 3}
	\large{\textbf{Sprint 3 - Successes}}
	\begin{itemize}
		\item Many SITL simulations
		\item Working image homography code
		\item Assembled Frame, Motors, ESC's
	\end{itemize}
	\large{\textbf{Sprint 3 - Setbacks}}
	\begin{itemize}
		\item Pixhawk delayed 2 weeks, build not completed
		\item SITL simulations rejected waypoint files
	\end{itemize}
\end{frame}
%%% End SECTION 1 


%% Begin SECTION 2 
\begin{frame}{Architecture}
PLACE HOLDER FOR THIS STUFF:
Architecture, Design, Technical Aspects, Data structures, Data ow, Communications, Tools
\end{frame}

% Include Architecture/Design/Tech Specs/& Tools ---Likely will take a few slides 
\begin{frame}{UAV Design \& Tech Specs}

\end{frame}

% Include Architecture/Design/Tech Specs/& Tools ---Likely will take a few slides 
\begin{frame}{Visual Homography Design \& Tech Specs}

\end{frame}

% Include Architecture/Design/Tech Specs/& Tools ---Likely will take a few slides 
\begin{frame}{Simulation Design \& Tech Specs}

\end{frame}

%% END SECTION 2


%% BEGIN SECTION 3
\begin{frame}{Testing}
PLACE HOLDER FOR THIS STUFF:
Unit or Component Testing,  System Testing,  System Integration,  Remaining backlog,  Revised goals
and Revised Deliverable
\end{frame}

% How are we going to test the UAV 
\begin{frame}{UAV Testing}

Manual Flight \\
Autonomous Flight \\

\end{frame}

% How are we going to test the VH Landing Algorithm
% Maybe discuss tests at the different stages (blob color recog, dist/dir output, real-time output (How many frames?)) 
\begin{frame}{Visual Homography Landing Testing}

\end{frame}

% How do we plan to integrate the different systems together
\begin{frame}{Integration}

\end{frame}


\begin{frame}{Remaining Backlog}

\end{frame}


\begin{frame}{Revised Goals}

\end{frame}


%% END SECTION 3


%% BEGIN SECTION 4
\begin{frame}{Successes and Issues}
PLACE HOLDER FOR THIS STUFF:
Successes (goals met), Issues or problems (goals not met), Risk Analysis, Risk Mitigation, Timeline,
Budget/costs, Intellectual Property Aspects, Licensing
\end{frame}

\begin{frame}{Successes}

Parts are now in!!



\end{frame}

\begin{frame}{Issues}

Parts are now in!! (Our UAV build has been delayed by a semester)

Simulation integration issues

Large Dependencies (If someone's awesomely helpful interface fails or is buggy, we need to address how we can work around it).

\end{frame}

\begin{frame}{Risk Analysis}

\end{frame}

\begin{frame}{Risk Mitigation}

\end{frame}

\begin{frame}{IP \& Licensing}

\end{frame}

%% END SECTION 4


%% BEGIN SECTION 5
\begin{frame}{Prototypes and Demos}
PLACE HOLDER FOR THIS STUFF:
Demos!!
\end{frame}

%% END SECTION 5
\begin{frame}{ END}
\end{frame}



\end{document}
